Fig1

### 2020-05-15 analysis/figure-1.Rmd
fig 1 still working yea
changed axes

```{r}
allDEG <- read_csv("../results/03_allDEG.csv")
str(allDEG)
unique(allDEG$comparison)
```

@@

# hyp
d2 <- makebargraph("hypothalamus","DEGs w/ + LFC", 0, 4300) + 
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank())  +
  labs(subtitle = " ")
# pit
d4 <- makebargraph("pituitary","DEGs w/ + LFC", 0, 4300)  +  
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())  +
  labs(subtitle = " ")
# gon
d6 <- makebargraph("gonad","DEGs w/ + LFC", 0, 4300) +  
  theme(axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabelschar)+
  labs(subtitle = " ")

>>>>

```{r}
allDEG <- read_csv("../results/03_allDEGs.csv") %>%
  mutate(comparison = factor(comparison, levels = comparisonlevelschar))
str(allDEG)
unique(allDEG$comparison)
```

@@

# hyp
d2 <- makebargraph("hypothalamus","DEGs w/ + LFC", 0, 4500) + 
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank())  +
  labs(subtitle = " ")
# pit
d4 <- makebargraph("pituitary","DEGs w/ + LFC", 0, 4500)  +  
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())  +
  labs(subtitle = " ")
# gon
d6 <- makebargraph("gonad","DEGs w/ + LFC", 0, 4500) +  
  theme(axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabelschar)+
  labs(subtitle = " ")
